\documentclass{article}
\usepackage{amsthm}
\begin{document}
\section{}
We will use Trie as our underlying database, with some slight modifications. The Trie tree nodes will also have a rank, the rank is a bool
which indicates whether there are any words that are subwords of other words
in it's subtree(the subtree that has that node as it's root).
We will also store a flag indicating whether there are any words in the 
database that are subwords of other words in the database - note that
this is in fact a rank, it is determined by whether the letter stored
in the node is the end of a word, which is a matter of checking if it has a \$ child(in which case, it is a subword iff the node has letter children) and whether children have a subword in their subtree.
Now the root of the whole tree will indicate whether the database has any subwords.
If we want to allow duplications, we could store a counter in the \$ nodes, to indicate how many words end in it's parent letter and then determine the rank using that(if we want words to be subwords of identical words we would condsider a counter of 2 or more to indicate a subword in addition to the previous indications). 
\subsection*{Insert}
We will insert the word as normal, when we finish, we will go over the path, top to bottom and update the ranks. We have $O(|s|)$ operations for the normal insertion route, and $O(|s|)$ operations to update the ranks(updating a single rank is O(1), and we do it |s| times), and so we have $O(|s|)$ time complexity.
\subsection*{Remove}
We will remove the word as normal, then update the ranks along it's path top to bottom again, and so we have $O(|s|)$ time complexity for the same reason as insert.
\subsection*{PrefixExists}
Returns the rank of the root of the tree, we always have that stored and so this takes O(1) time complexity.
\section{}
No need to modify the rest of the data structure.\\
We will simply search for s in the Trie tree, then when we find it(If we are unable to traverse the tree until we reaches s's final letter, we return false, as a it cannot be a subword of a any other word if there are no words beginning in it's letters), we will return the rank of the node's final letter.
There exists $s_1, s_2$ such that s is a subword of $s_1$ which is a subword of $s_2$, iff if the rank of the final letter is ln, as a rank of node is turned on only if some word in it's subtree is a subword of another word in it's subtree, and s would be a subword of the original word.\\
The search takes $O(|s|)$, checking the ranks is O($|\Sigma |O(1)$)=O(1), meaning we have $O(|s|)$ time complexity.
\end{document}
